POMDP comparisons across sigma_m, sigma_g

### 2017-10-10 appendix/appendix.Rmd
tweaks for savio
analytic checks only if discount = 1

@@

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 1
```

@@

### Optional checks:

```{r}
## Make sure these match the known analytic solutions for Graham-Schaefer model:
testthat::expect_equal(B_MSY, K / 2)
testthat::expect_equal(MSY, r * K / 4)
testthat::expect_equal(F_MSY, r / 2)
```

>>>>

```{r}
options(mc.cores=9)
```

@@

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99
```

@@

```{r optional_checks}
## Make sure these match the known analytic solutions for Graham-Schaefer model (only true of discount = 1)
if(discount == 1){
  testthat::expect_equal(B_MSY, K / 2)
  testthat::expect_equal(MSY, r * K / 4)
  testthat::expect_equal(F_MSY, r / 2)
}
```
